---
title: "DSA Assignment"
author: "Sunny Sharma"
date: "18/12/2020"
output: word_document
---

Object creation & Value assignment
```{r}
a=25
b=30
```

Command line Interface
```{r}
b
```

Object need not be explicitly defined
```{r}
c=45
class(c)
d=TRUE
class(d)
```
Simple Mathematical Operations:

1) Addition
```{r}
a+b
```
2)Subtraction
```{r}
b-a
```
3) Division
```{r}
b/a
```
4) Multiplication
```{r}
b*a
```
5) Square root
```{r}
sqrt(a)
```
6) Power
```{r}
a^3
```
7)logarithm 
```{r}
log(a,base=exp(1))
```
8) Factorial
```{r}
factorial(a)
```

Data types are as follows:

1) Numeric
```{r}
a=20
class(a)
```
2)Character
```{r}
b="Hello"
class(b)
```
3) Logical
```{r}
c=TRUE
class(c)
d=FALSE
class(d)
```
4) Date
```{r}
date1=as.Date("2015-04-16")
class(date1)
```
5)POSIXct - Date & Time
```{r}
date2=as.POSIXct("2015-5-18 16:32")
class(date2)
```

Factors

```{r}
rm(list=ls())
a=c("jan","feb","mar","apr")
a
as.numeric(a)
class(a)
b=as.factor(a)
as.numeric(b)
b
# Missing Value test
c=c(1,2,3,NA,NA,5)
is.na(c)
d=c("jan",NA,"feb")
is.na(d)
# Null value
e=c(NULL,3,4)
is.null(e)
f=NULL
is.null(f)
```

TO get a working directory
```{r}
getwd()
```

Divider Function
```{r}
divider = function(x,y)
{
  result = x/y
  print(result)
}
divider(100,20)
```
Multiplier Function
```{r}
multiply = function(x,y)
{
  result = x*y
  print(result)
}
multiply(8,20)
```
Concatenation and Arrays
```{r}
d=c(1:5)
d
d+6
d-2
```
R is a vectorized language
```{r}
e=c(1:10)
e
f=e*2
f
g=f/2
g
```
Matrix Creation
```{r}
M=matrix(1:15,nrow=3)
M
```

```{r}
a=matrix(1:10,nrow=5)
b=matrix(11:20,nrow=2)
a
b
# Matrix addition
c=t(b)
a+c
# Matrix Multiplication
a%*%b
```

Arrays (N dimensional)
```{r}
d=array(1:16, dim=c(4,2,2))
d
d[,,2]
d[,1,1]
```

```{r}
url=read.table("C:\\Users\\Admin\\Documents\\R\\Tomato First.csv",header=TRUE,sep=",")
head(url)
```

Loading Built in data sets
```{r}
data("mtcars")
head(mtcars, 7)
```

```{r}
# Generate a random sample
d=sample(x=1:25,size=50,replace=TRUE)
d
mean(d)
# Weighted means
grade=c(95,92,91,87)
weights= c(1/2,1/4,1/8,1/8)
mean(grade)
weighted.mean(x=grade,w=weights)
# Variance & SD
var(d)
sd(x=d,na.rm=FALSE)
# Min & Max Functions
min(d)
max(d)
median(d)
quantile(d,probs=c(0.2,0.4,0.6,0.8))
```
```{r}
library("ggplot2")
head(economics)
# Covariance
cor(economics$pce,economics$psavert)
```

```{r}
rm(list=ls())
data(tips, package="reshape2")
head(tips)
str(tips)
# Returns Unique values
unique(tips$sex)
unique(tips$day)
# one sample t test (H0 = 2.5, Two Tailed)
t.test(tips$tip, alternative="two.sided",mu=2.5)
# one sample t test (H0 = 2.5, upper tail)
t.test(tips$tip, alternative="greater",mu=2.5)
  
# Two sample t test 
t.test(tip~sex, data=tips, var.equal = TRUE)
# Anova
tipAnova=aov(tip~day,tips)
summary(tipAnova)
```

Vector Creation
```{r}
a=c(1:15)
a
```
Vector Operation
```{r}
a+3
a-2
a^2
b=c(-4:0)
a+b
d=c(-4:10)
a
d
any(a<d)
all(a<d)
a[4]
f=c("january","february","march","april","may","june")
nchar(f)
```
Naming Vectors
```{r}
c(one="a",two="b",three="c")
w=1:3
names(w)=c("a","b","c")
w
```

